Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-04 RR_manuscript/Draft_RR.tex
♻️ - fix typos listed in #282

\author{Stefano Coretta*\affilnum{1, 2}, Joseph V. Casillas\affilnum{3}, Simon Roessig\affilnum{}, Michael Franke\affilnum{}, Ali H. Al-Hoorie\affilnum{}, Jalal Al-Tamimi\affilnum{}, Najd E. Alotaibi\affilnum{}, Mohammed K. AlShakhori\affilnum{}, Ruth M. Altmiller\affilnum{}, Pablo Arantes\affilnum{}, Angeliki Athanasopoulou\affilnum{}, Melissa M. Baese-Berk\affilnum{}, George Bailey\affilnum{}, Cheman Baira A Sangma\affilnum{}, Eleonora J. Beier\affilnum{}, Gabriela M. Benavides\affilnum{}, Nicole Benker\affilnum{}, Emelia P. BensonMeyer\affilnum{}, Nina R. Benway\affilnum{}, Grant M. Berry\affilnum{}, Liwen Bing\affilnum{}, Christina Bjorndahl\affilnum{}, Mariska Bolyanatz\affilnum{}, Aaron Braver\affilnum{}, Violet A. Brown\affilnum{}, Alicia M. Brown\affilnum{}, Alejna Brugos\affilnum{}, Erin M. Buchanan\affilnum{}, Tanna Butlin\affilnum{}, Andrés Buxó-Lugo\affilnum{}, Coline Caillol\affilnum{}, Francesco Cangemi\affilnum{}, Christopher Carignan\affilnum{}, Sita Carraturo\affilnum{}, Tiphaine Caudrelier\affilnum{}, Eleanor Chodroff\affilnum{}, Michelle Cohn\affilnum{}, Johanna Cronenberg\affilnum{}, Olivier Crouzet\affilnum{}, Erica L. Dagar\affilnum{}, Charlotte Dawson\affilnum{}, Carissa A. Diantoro\affilnum{}, Marie Dokovova\affilnum{}, Wood Drake\affilnum{}, Fengting Du\affilnum{}, Margaux Dubuis\affilnum{}, Florent Duême\affilnum{}, Matthew Durward\affilnum{}, Ander Egurtzegi\affilnum{}, Mahmoud M. Elsherif\affilnum{}, Janina Esser\affilnum{}, Emmanuel Ferragne\affilnum{}, Fernanda Ferreira\affilnum{}, Lauren K. Fink\affilnum{}, Sara Finley\affilnum{}, Kurtis Foster\affilnum{}, Paul Foulkes\affilnum{}, Rosa Franzke\affilnum{}, Gabriel Frazer-McKee\affilnum{}, Robert Fromont\affilnum{}, Christina García\affilnum{}, Jason Geller\affilnum{}, Camille L. Grasso\affilnum{}, Pia Greca\affilnum{}, Martine Grice\affilnum{}, Magdalena S. Grose-Hodge\affilnum{}, Amelia J. Gully\affilnum{}, Caitlin Halfacre\affilnum{}, Westerbeek Hans\affilnum{}, Ivy Hauser\affilnum{}, Jen Hay\affilnum{}, Robert Haywood\affilnum{}, Sam Hellmuth\affilnum{}, Allison I. Hilger\affilnum{}, Nicole Holliday\affilnum{}, Damar Hoogland\affilnum{}, Yaqian Huang\affilnum{}, Vincent Hughes\affilnum{}, Ane Icardo Isasa\affilnum{}, Zlatomira G. Ilchovska\affilnum{}, Hae-Sung Jeon\affilnum{}, Jacq Jones\affilnum{}, Mágat N. Junges\affilnum{}, Stephanie Kaefer\affilnum{}, Constantijn Kaland\affilnum{}, Matthew C. Kelley\affilnum{}, Niamh E. Kelly\affilnum{}, Ghada Khattab\affilnum{}, Emiel Krahmer\affilnum{}, Dorota Krajewska\affilnum{}, Andreas Krug\affilnum{}, Abhilasha A. Kumar\affilnum{}, Anna Lander\affilnum{}, Tomas O. Lentz\affilnum{}, Wanyin Li\affilnum{}, Yanyu Li\affilnum{}, Maria Lialiou\affilnum{}, Ronaldo M. Lima Jr.\affilnum{}, Justin J. H. Lo\affilnum{}, Julio César López Otero\affilnum{}, Bradley Mackay\affilnum{}, Bethany MacLeod\affilnum{}, Mel Mallard\affilnum{}, Carol-Ann McConnellogue\affilnum{}, George Moroz\affilnum{}, Mridhula Murali\affilnum{}, Ladislas Nalborczyk\affilnum{}, Filip Nenadić\affilnum{}, Jessica Nieder\affilnum{}, Dušan Nikolić\affilnum{}, Francisco G. S. Nogueira\affilnum{}, Heather M. Offerman\affilnum{}, Elisa Passoni\affilnum{}, Maud Pélissier\affilnum{}, Scott J. Perry\affilnum{}, Alexandra M. Pfiffner\affilnum{}, Michael Proctor\affilnum{}, Ryan Rhodes\affilnum{}, Nicole Rodríguez\affilnum{}, Elizabeth Roepke\affilnum{}, Jan P. Röer\affilnum{}, Koolen Ruud\affilnum{}, Lucia Sbacco\affilnum{}, Rebecca Scarborough\affilnum{}, Felix Schaeffler\affilnum{}, Erik Schleef\affilnum{}, Dominic Schmitz\affilnum{}, Alexander Shiryaev\affilnum{}, Márton Sóskuthy\affilnum{}, Malin Spaniol\affilnum{}, Joseph A. Stanley\affilnum{}, Alyssa Strickler\affilnum{}, Alessandro Tavano\affilnum{}, Fabian Tomaschek\affilnum{}, Benjamin V. Tucker\affilnum{}, Rory Turnbull\affilnum{}, Kingsley Ugwuanyi\affilnum{}, Iñigo Urrestarazu-Porta\affilnum{}, Ruben van de Vijver\affilnum{}, Kristin J. Van Engen\affilnum{}, Emiel van Miltenburg\affilnum{}, Bruce Wang\affilnum{}, Natasha Warner\affilnum{}, Simon Wehrle\affilnum{}, Seth Wiener\affilnum{}, Stephen Winters\affilnum{}, Sidney G.-J. Wong\affilnum{}, Anna Wood\affilnum{}, Jane Wottawa\affilnum{}, Chenzi Xu\affilnum{}, Germán Zárate-Sández\affilnum{}, Georgia Zellou\affilnum{}, Cong Zhang\affilnum{}, Jian Zhu\affilnum{}, Timo B. Roettger\affilnum{4}}

\affiliation{\affilnum{1}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{2}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{4}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}

@@

We had initially planned to also include a measure of conservativeness of the model specification, as the number of random/group-level effects included and the number of post-hoc changes to the acoustic measurements the teams reported to have carried out.
When fitting the model, we realized that the measure of conservativeness is related to the standard error of the estimates (i.e.~more group-level effects = higher standard error).
Moreover, there was no team that declared to have made post-hoc changes to the analyses, this we decided against including these two preregistered predictors in the model.

@@

The mean of the number of different predictors included in teams' models was 2 (defined as variables or columns in the data table).
This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = 1-\texttt{r}round(predictor\_n\$max\_predictor,1)`).
Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.

@@

The question arises whether these unique analysis pipelines led to different conclusions.
Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
Of the 104 submitted models, 37 were reported to show a statistically reliable effect (21.8\%).

@@

Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored.
Crowd-sourcing is limited by the sampled analysts and their biases.
Multiverse analyses are limited even further by the group of researchers who define possible analytic pathways.
Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
Possible tools to strengthen theoretical development are relate to mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.

@@

See \url{https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy.png}.

>>>>

\author{Stefano Coretta*\affilnum{1, 2}, Joseph V. Casillas\affilnum{3}, Simon Roessig\affilnum{4}, Michael Franke\affilnum{5}, Byron Ahn\affilnum{6}, Ali H. Al-Hoorie\affilnum{7}, Jalal Al-Tamimi\affilnum{8}, Najd E. Alotaibi\affilnum{9}, Mohammed K. AlShakhori\affilnum{10}, Ruth M. Altmiller\affilnum{11}, Pablo Arantes\affilnum{12}, Angeliki Athanasopoulou\affilnum{13}, Melissa M. Baese-Berk\affilnum{14}, George Bailey\affilnum{15}, Cheman Baira A Sangma\affilnum{16}, Eleonora J. Beier\affilnum{17}, Gabriela M. Benavides\affilnum{18}, Nicole Benker\affilnum{19}, Emelia P. BensonMeyer\affilnum{20}, Nina R. Benway\affilnum{21}, Grant M. Berry\affilnum{22}, Liwen Bing\affilnum{23}, Christina Bjorndahl\affilnum{24}, Mariska Bolyanatz\affilnum{25}, Aaron Braver\affilnum{26}, Violet A. Brown\affilnum{27}, Alicia M. Brown\affilnum{28}, Alejna Brugos\affilnum{29}, Erin M. Buchanan\affilnum{30}, Tanna Butlin\affilnum{31}, Andrés Buxó-Lugo\affilnum{32}, Coline Caillol\affilnum{33}, Francesco Cangemi\affilnum{34}, Christopher Carignan\affilnum{35}, Sita Carraturo\affilnum{36}, Tiphaine Caudrelier\affilnum{37}, Eleanor Chodroff\affilnum{38}, Michelle Cohn\affilnum{39}, Johanna Cronenberg\affilnum{40}, Olivier Crouzet\affilnum{41}, Erica L. Dagar\affilnum{42}, Charlotte Dawson\affilnum{43}, Carissa A. Diantoro\affilnum{44}, Marie Dokovova\affilnum{45}, Shiloh Drake\affilnum{46}, Fengting Du\affilnum{47}, Margaux Dubuis\affilnum{48}, Florent Duême\affilnum{49}, Matthew Durward\affilnum{50}, Ander Egurtzegi\affilnum{51}, Mahmoud M. Elsherif\affilnum{52}, Janina Esser\affilnum{53}, Emmanuel Ferragne\affilnum{54}, Fernanda Ferreira\affilnum{55}, Lauren K. Fink\affilnum{56}, Sara Finley\affilnum{57}, Kurtis Foster\affilnum{58}, Paul Foulkes\affilnum{59}, Rosa Franzke\affilnum{60}, Gabriel Frazer-McKee\affilnum{61}, Robert Fromont\affilnum{62}, Christina García\affilnum{63}, Jason Geller\affilnum{64}, Camille L. Grasso\affilnum{65}, Pia Greca\affilnum{66}, Martine Grice\affilnum{67}, Magdalena S. Grose-Hodge\affilnum{68}, Amelia J. Gully\affilnum{69}, Caitlin Halfacre\affilnum{70}, Ivy Hauser\affilnum{71}, Jen Hay\affilnum{72}, Robert Haywood\affilnum{73}, Sam Hellmuth\affilnum{74}, Allison I. Hilger\affilnum{75}, Nicole Holliday\affilnum{76}, Damar Hoogland\affilnum{77}, Yaqian Huang\affilnum{78}, Vincent Hughes\affilnum{79}, Ane Icardo Isasa\affilnum{80}, Zlatomira G. Ilchovska\affilnum{81}, Hae-Sung Jeon\affilnum{82}, Jacq Jones\affilnum{83}, Mágat N. Junges\affilnum{84}, Stephanie Kaefer\affilnum{85}, Constantijn Kaland\affilnum{86}, Matthew C. Kelley\affilnum{87}, Niamh E. Kelly\affilnum{88}, Thomas Kettig\affilnum{89}, Ghada Khattab\affilnum{90}, Ruud Koolen\affilnum{91}, Emiel Krahmer\affilnum{92}, Dorota Krajewska\affilnum{93}, Andreas Krug\affilnum{94}, Abhilasha A. Kumar\affilnum{95}, Anna Lander\affilnum{96}, Tomas O. Lentz\affilnum{97}, Wanyin Li\affilnum{98}, Yanyu Li\affilnum{99}, Maria Lialiou\affilnum{100}, Ronaldo M. Lima Jr.\affilnum{101}, Justin J. H. Lo\affilnum{102}, Julio Cesar Lopez Otero\affilnum{103}, Bradley Mackay\affilnum{104}, Bethany MacLeod\affilnum{105}, Mel Mallard\affilnum{106}, Carol-Ann Mary McConnellogue\affilnum{107}, George Moroz\affilnum{108}, Mridhula Murali\affilnum{109}, Ladislas Nalborczyk\affilnum{110}, Filip Nenadić\affilnum{111}, Jessica Nieder\affilnum{112}, Dušan Nikolić\affilnum{113}, Francisco G. S. Nogueira\affilnum{114}, Heather M. Offerman\affilnum{115}, Elisa Passoni\affilnum{116}, Maud Pélissier\affilnum{117}, Scott J. Perry\affilnum{118}, Alexandra M. Pfiffner\affilnum{119}, Michael Proctor\affilnum{120}, Ryan Rhodes\affilnum{121}, Nicole Rodríguez\affilnum{122}, Elizabeth Roepke\affilnum{123}, Jan P. Röer\affilnum{124}, Lucia Sbacco\affilnum{125}, Rebecca Scarborough\affilnum{126}, Felix Schaeffler\affilnum{127}, Erik Schleef\affilnum{128}, Dominic Schmitz\affilnum{129}, Alexander Shiryaev\affilnum{130}, Márton Sóskuthy\affilnum{131}, Malin Spaniol\affilnum{132}, Joseph A. Stanley\affilnum{133}, Alyssa Strickler\affilnum{134}, Alessandro Tavano\affilnum{135}, Fabian Tomaschek\affilnum{136}, Benjamin V. Tucker\affilnum{137}, Rory Turnbull\affilnum{138}, Kingsley O. Ugwuanyi\affilnum{139}, Iñigo Urrestarazu-Porta\affilnum{140}, Ruben van de Vijver\affilnum{141}, Kristin J. Van Engen\affilnum{142}, Emiel van Miltenburg\affilnum{143}, Bruce Wang\affilnum{144}, Natasha Warner\affilnum{145}, Simon Wehrle\affilnum{146}, Hans Westerbeek\affilnum{147}, Seth Wiener\affilnum{148}, Stephen Winters\affilnum{149}, Sidney G.-J. Wong\affilnum{150}, Anna Wood\affilnum{151}, Jane Wottawa\affilnum{152}, Chenzi Xu\affilnum{153}, Germán Zárate-Sández\affilnum{154}, Georgia Zellou\affilnum{155}, Cong Zhang\affilnum{156}, Jian Zhu\affilnum{157}, Timo B. Roettger\affilnum{158}}

\affiliation{\affilnum{1, 2}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, United States}\\\affilnum{4}{Department of Linguistics, Cornell University, United States}\\\affilnum{5}{Department of General and Computational Linguistics, University of Tübingen, Germany}\\\affilnum{6}{Program in Linguistics, Princeton University, United States}\\\affilnum{7}{Jubail English Language and Preparatory Year Institute, Royal Commission for Jubail and Yanbu, Saudi Arabia}\\\affilnum{8}{Laboratoire de Lingusitique Formelle (LLF), CNRS, Université Paris Cité, France}\\\affilnum{9}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{10}{Department of Linguistics, University of Arizona, United States}\\\affilnum{11}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{12}{Departamento de Letras, Universidade Federal de São Carlos, Brazil}\\\affilnum{13}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{14}{Department of Linguistics, University of Oregon, United States}\\\affilnum{15}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{16}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{17}{Department of Psychology, University of California, Davis, United States}\\\affilnum{18}{Department of Linguistics, University of Arizona, United States}\\\affilnum{19}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{20}{University of Pennsylvania, United States}\\\affilnum{21}{Department of Communication Sciences and Disorders, Syracuse University, United States}\\\affilnum{22}{Department of Spanish, Villanova University, United States}\\\affilnum{23}{Department of English Language and Linguistics, University of Birmingham, United Kingdom}\\\affilnum{24}{Department of Philosophy, Carnegie Mellon University, United States}\\\affilnum{25}{Department of Spanish \& French Studies, Occidental College, United States}\\\affilnum{26}{Department of English, Texas Tech University, United States}\\\affilnum{27}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{28}{Department of Spanish and Portuguese, University of Arizona, United States}\\\affilnum{29}{Division of Mathematics and Computer Science, Simmons University, United States}\\\affilnum{30}{Analytics, Harrisburg University of Science and Technology, United States}\\\affilnum{31}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{32}{Department of Psychology, University at Buffalo, SUNY, United States}\\\affilnum{33}{Université Paris Cité, France}\\\affilnum{34}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{35}{Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom}\\\affilnum{36}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{37}{Basque Center on Cognition Brain and Language, Spain}\\\affilnum{38}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{39}{Department of Linguistics, University of California, Davis, United States}\\\affilnum{40}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{41}{LLING, UMR6310, Nantes Université / CNRS, France}\\\affilnum{42}{Department of Linguisticss and TESOL, University of Texas at Arlington, United States}\\\affilnum{43}{School of Psychology, Newcastle University, United Kingdom}\\\affilnum{44}{Department of Linguistics, University of Oregon, United States}\\\affilnum{45}{School of Psychological Sciences and Health, University of Strathclyde, United Kingdom}\\\affilnum{46}{Department of Linguistics, University of Oregon, United States}\\\affilnum{47}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{48}{Department of comparative language science, Universität Zürich, Swizerland, Switzerland}\\\affilnum{49}{Basque Center on Cognition Brain and Language, Spain}\\\affilnum{50}{Department of Linguistics, University of Canterbury, New Zealand}\\\affilnum{51}{IKER (UMR 5478), Centre National de la Recherche Scientifique (CNRS), France}\\\affilnum{52}{Department of Neuroscience, Psychology and Behaviour, University of Leicester, United Kingdom}\\\affilnum{53}{Statistics Group, Association for Diversity in Linguistics, Germany}\\\affilnum{54}{CLILLAC-ARP, Université Paris Cité, France}\\\affilnum{55}{Department of Psychology, University of California, Davis, United States}\\\affilnum{56}{Department of Music, Max Planck Institute for Empirical Aesthetics, Germany}\\\affilnum{57}{Department of Psychology, Pacific Lutheran University, United States}\\\affilnum{58}{Department of Linguistics, University of Oregon, United States}\\\affilnum{59}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{60}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{61}{Department of languages, linguistics, and translation, Université Laval, Canada}\\\affilnum{62}{New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand}\\\affilnum{63}{Department of Languages, Literatures, and Cultures, Saint Louis University, United States}\\\affilnum{64}{Department of Psychology, Princeton University, United States}\\\affilnum{65}{LPC, Aix Marseille Univ, CNRS, France}\\\affilnum{66}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{67}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{68}{Department of English Language and Linguistics, University of Birmingham, United Kingdom}\\\affilnum{69}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{70}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{71}{Department of Linguistics and TESOL, University of Texas at Arlington, United States}\\\affilnum{72}{New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand}\\\affilnum{73}{Ao Tawhiti Unlimited Discovery, New Zealand}\\\affilnum{74}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{75}{Department of Speech, Language, and Hearing Sciences, University of Colorado Boulder, United States}\\\affilnum{76}{Department of Linguistics and Cognitive Science, Pomona College, United States}\\\affilnum{77}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{78}{University of California, Los Angeles, United States}\\\affilnum{79}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{80}{Department of Modern and Classical Languages and Literatures, California State University, Northridge, United States}\\\affilnum{81}{School of Psychology, University of Birmingham, United Kingdom}\\\affilnum{82}{School of Humanities, Language and Global Studies, University of Central Lancashire, United Kingdom}\\\affilnum{83}{Department of Linguistics, University of Canterbury, Aotearoa}\\\affilnum{84}{Programa de Pós-Graduação em Letras, Federal University of Rio Grande do Sul, Brazil}\\\affilnum{85}{Department of Linguistics, University of Canterbury, New Zealand}\\\affilnum{86}{Institute of Linguistics, University of Cologne, Germany}\\\affilnum{87}{Department of Linguistics, University of Washington, United States}\\\affilnum{88}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{89}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{90}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{91}{Department of Communication and Cognition, Tilburg University, Netherlands}\\\affilnum{92}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{93}{Department of Linguistics and Basque Studies, University of the Basque Country UPV/EHU, Spain}\\\affilnum{94}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{95}{Department of Psychology, Bowdoin College, ME, United States}\\\affilnum{96}{Linguistic Convergence Laboratory, HSE University, Russia}\\\affilnum{97}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{98}{School of Psychology, University of Birmingham, United Kingdom}\\\affilnum{99}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{100}{Institute of German Language I Linguistics, University of Cologne, Germany}\\\affilnum{101}{Department of English Language Studies, Federal University of Ceará, Brazil}\\\affilnum{102}{Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom}\\\affilnum{103}{Department of Hispanic Studies, University of Houston, United States}\\\affilnum{104}{Department of English and American Studies, University of Salzburg, Austria}\\\affilnum{105}{School of Linguistics \& Language Studies, Carleton University, Canada}\\\affilnum{106}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{107}{Population Health Sciences Institute - Faculty of Medical Sciences, Newcastle University, United Kingdom}\\\affilnum{108}{HSE University, Russia}\\\affilnum{109}{Speech and Language Therapy, University of Strathclyde, United Kingdom}\\\affilnum{110}{LPC, Aix Marseille Univ, CNRS, France}\\\affilnum{111}{Department of Psychology, Faculty of Media and Communications, Singidunum University, Serbia}\\\affilnum{112}{Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany}\\\affilnum{113}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{114}{Graduate Program in Linguistics, Federal University of Ceará, Brazil}\\\affilnum{115}{World Languages, Literatures and Cultures Department, University of Arkansas, United States}\\\affilnum{116}{Deparment of Linguistics, Queen Mary University of London, United Kingdom}\\\affilnum{117}{CLILLAC-ARP, Université Paris Cité, France}\\\affilnum{118}{Department of Linguistics, University of Alberta, Canada}\\\affilnum{119}{Department of Linguistics, University of California, Berkeley, United States}\\\affilnum{120}{Department of Linguistics, Macquarie University, Australia}\\\affilnum{121}{Center for Cognitive Science, Rutgers University, United States}\\\affilnum{122}{Department of Spanish and Portuguese, Rutgers University, United States}\\\affilnum{123}{Department of Speech, Language, and Hearing Sciences, Saint Louis University, United States}\\\affilnum{124}{Department of Psychology, Witten/Herdecke University, Germany}\\\affilnum{125}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{126}{Department of Linguistics, University of Colorado Boulder, United States}\\\affilnum{127}{Clinical Audiology, Speech and Language (CASL) Research Centre, Queen Margaret University Edinburgh, United Kingdom}\\\affilnum{128}{Department of English and American Studies, University of Salzburg, Austria}\\\affilnum{129}{Department of English and American Studies, Heinrich Heine University Düsseldorf, Germany}\\\affilnum{130}{Linguistic Convergence Laboratory, HSE University, Russia}\\\affilnum{131}{Department of Linguistics, University of British Columbia, Canada}\\\affilnum{132}{Department of Psychiatry and Psychotherapy, University Hospital Cologne, Germany}\\\affilnum{133}{Department of Linguistics, Brigham Young University, United States}\\\affilnum{134}{Department of Linguistics, University of Colorado Boulder, United States}\\\affilnum{135}{Department of Neuroscience, Max Planck Institute for Empirical Aesthetics, Germany}\\\affilnum{136}{Department of General Linguistics, University of Tübingen, Germany}\\\affilnum{137}{Department of Linguistics, University of Alberta, Canada}\\\affilnum{138}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{139}{Department of English \& Literary Studies, University of Nigeria, Nsukka, Nigeria}\\\affilnum{140}{IKER-UMR5478, Centre National de la Recherche Scientifique (CNRS), France}\\\affilnum{141}{Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany}\\\affilnum{142}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{143}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{144}{Chinese and Bilingual Studies, Hong Kong Polytechnic University, Hong Kong SAR, China}\\\affilnum{145}{Department of Linguistics, University of Arizona, United States}\\\affilnum{146}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{147}{Department of Languages, Literature and Communication, Utrecht University, Netherlands}\\\affilnum{148}{Department of Modern Languages, Carnegie Mellon University, United States}\\\affilnum{149}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{150}{Geospatial Research Institute, University of Canterbury, New Zealand}\\\affilnum{151}{Department of Linguistics, University of Oregon, United States}\\\affilnum{152}{Département de Lettres modernes, LIUM, LST, Le Mans Université, France}\\\affilnum{153}{NA, University of Oxford, United Kingdom}\\\affilnum{154}{Department of Spanish, Western Michigan University, United States}\\\affilnum{155}{Department of Linguistics, University of California, Davis, United States}\\\affilnum{156}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{157}{School of Information, University of Michigan, Ann Arbor, United States}\\\affilnum{158}{Department of Linguistics and Scandinavian Studies, University of Oslo, Norway}}

@@

We had initially planned to also include a measure of conservativeness of the model specification, as the number of random/group-level effects included and the number of post-hoc changes to the acoustic measurements the teams reported to have carried out.
When fitting the model, we realized that the measure of conservativeness is related to the standard error of the estimates (i.e.~more group-level effects = higher standard error).
Moreover, there was no team that declared to have made post-hoc changes to the analyses, thus we decided against including these two preregistered predictors in the model.

@@

The mean of the number of different predictors included in teams' models was 2 (defined as variables or columns in the data table).
This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = -4).
Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.

@@

The question arises whether these unique analysis pipelines led to different conclusions.
Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
Of the 170 critical model coefficients, 37 were claimed to show a statistically reliable effect (21.8\%).

@@

Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored.
Crowd-sourcing is limited by the sampled analysts and their biases.
Multiverse analyses are limited even further by the group of researchers who define possible analytic pathways.
Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
Possible tools to strengthen theoretical development are related to mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.

@@

See \url{https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy-all.png}.
